Liveness-Based Garbage Collection for Lazy Languages

### 2016-04-14 paper/cfg-to-nfa.tex
Updated NFA example automata

 \begin{wrapfigure}{r}{0.25\textwidth}
%\begin{figure}[t!]
\scalebox{0.5}{
  \begin{tabular}{cc}
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-3)(50,12)
  \putnode{t0}{origin}{5}{0}{\var{\Df{\length}{1}}} \putnode{t1}{t0}{15}{0}{\pscirclebox{\mbox{\ \ \ \
  }}} \hspace{5mm} \putnode{t2}{t1}{15}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \
  }}} \psset{arrows=->} \ncline{t0}{t1} \ncline{t1}{t2} \putnode{l0}{t1}{7}{2}{\clazy} \nccurve[angleA=45,
  angleB=135,                                                 ncurv=4,
  nodesep=-1]{t1}{t1} \putnode{l1}{t1}{0}{8}{\acdr, \clazy} \nccurve[angleA=45,
  angleB=135,                                                 ncurv=3,
  nodesep=-1]{t2}{t2} \putnode{l2}{t2}{0}{8}{\clazy}
\end{pspicture}
&
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-3)(30,12)
  \putnode{t0}{origin}{5}{0}{\var{\Df{\length}{1}}} \putnode{t1}{t0}{15}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \
  }}}     \psset{arrows=->}    \ncline{t0}{t1}     \nccurve[angleA=45,
  angleB=135,                                                 ncurv=3,
  nodesep=-1]{t1}{t1} \putnode{l1}{t1}{0}{8}{\acdr}
\end{pspicture}
\\
(a) & (b) \end{tabular}}
\caption{(a) The  grammar rules for \var{\Df{\length}{1}}
  converted      into      an      automaton     and      (b)      its
  DFA.}\label{fig:example-automata}
\vspace*{-2mm}
\figrule
%\end{figure}
\end{wrapfigure}
Figure~\ref{fig:example-automata}(a)  shows the  NFA that  is obtained
from the grammar for \var{\Df{\length}{1}}, and the final DFA is shown
in  Figure~\ref{fig:example-automata}(b).  This  expectedly says  that
for  a  demand  $\sigma_{\length}$,   the  liveness  of  the  argument
of \length\ is $\acdr^{*}$ (the spine of the list is traversed).

@@

\begin{wrapfigure}{r}{.25\textwidth}
\scalebox{0.5}{
\begin{tabular}{cc}
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(50,8) %\psframe(0,-5)(40,8)
  \putnode{t0}{origin}{5}{0}{\var{\Lanv{\pa}{}}} \putnode{t1}{t0}{9}{0}{\pscirclebox{\mbox{\ \ \ \
  }}} \hspace{5mm} \putnode{t2}{t1}{12}{0}{\pscirclebox{\mbox{\  \ \ \
  }}}
%  \putnode{t3}{t2}{12}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \ }}}
  \psset{arrows=->} \ncline{t0}{t1} \ncline{t1}{t2} \putnode{l0}{t1}{5}{2}{\clazy}
%  \ncline{t2}{t3}
%  \nccurve[angleA=55, angleB=125, ncurv=3, nodesep=-.8]{t3}{t3}
%  \putnode{l2}{tD1}{0}{10}{\acdr}
 \putnode{tD1}{t2}{12}{0}{\pscirclebox{\mbox{\       \       \       \
  }}} \hspace{5mm} \putnode{tD2}{tD1}{12}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \
  }}} \psset{arrows=->} \ncline{t2}{tD1} \putnode{l1}{t2}{5}{2}{\bcar} \ncline{tD1}{tD2} \putnode{lD0}{tD1}{5}{2}{\clazy} \nccurve[angleA=45,
  angleB=135,                                                 ncurv=4,
  nodesep=-1]{tD1}{tD1} \putnode{lD1}{tD1}{0}{8}{\acdr, \clazy} \nccurve[angleA=45,
  angleB=135,                                                 ncurv=3,
  nodesep=-1]{tD2}{tD2} \putnode{lD2}{tD2}{0}{8}{\clazy}
\end{pspicture}
&
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(20,8) %\psframe(0,-5)(40,8)
  \putnode{t0}{origin}{5}{0}{\var{\Lanv{\pa}{}}} \putnode{t1}{t0}{9}{0}{\pscirclebox{\mbox{\ \ \ \
  }}} \hspace{5mm} \psset{arrows=->} \ncline{t0}{t1}
\end{pspicture}
\\ 
(a) & (b)
\end{tabular}}
 \caption{(a) grammar  rules for \var{\Lanv{\pa}{}} converted  into an
  automation and (b) its DFA.}\label{fig:main1}
\end{wrapfigure}

>>>>

\begin{wrapfigure}{r}{0.25\textwidth}
\scalebox{0.5}{
          \begin{tabular}{cc}
          \psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
          \begin{pspicture}(0,-3)(50,12)
            \putnode{t0}{origin}{5}{0}{\var{\Df{\length}{1}}} \putnode{t1}{t0}{15}{0}{\pscirclebox{\mbox{\ \ \ \
  }}} \hspace{5mm} \putnode{t2}{t1}{15}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \
  }}} \psset{arrows=->} \ncline{t0}{t1} \ncline{t1}{t2} \putnode{l0}{t1}{7}{2}{\clazy} \nccurve[angleA=45,
  angleB=135,                                                 ncurv=4,
  nodesep=-1]{t1}{t1} \putnode{l1}{t1}{0}{8}{\acdr, \clazy} \nccurve[angleA=45,
  angleB=135,                                                 ncurv=3,
  nodesep=-1]{t2}{t2} \putnode{l2}{t2}{0}{8}{\clazy}
\end{pspicture}
&
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-3)(30,12)
  \putnode{t0}{origin}{5}{0}{\var{\Df{\length}{1}}} \putnode{t1}{t0}{15}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \
  }}}     \psset{arrows=->}    \ncline{t0}{t1}     \nccurve[angleA=45,
  angleB=135,                                                 ncurv=3,
  nodesep=-1]{t1}{t1} \putnode{l1}{t1}{0}{8}{\acdr}
\end{pspicture}
\\
(a) & (b)
 \end{tabular}}
\caption{(a) The  grammar rules for \var{\Df{\length}{1}}
  converted      into      an      automaton     and      (b)      its
  DFA.}\label{fig:example-automata}
\figrule
\vspace*{-5mm}
\end{wrapfigure}

Figure~\ref{fig:example-automata}(a)  shows the  NFA that  is obtained
from the grammar for \var{\Df{\length}{1}}, and the final DFA is shown
in  Figure~\ref{fig:example-automata}(b).  This  expectedly says  that
for  a  demand  $\sigma_{\length}$,   the  liveness  of  the  argument
of \length\ is $\acdr^{*}$ (the spine of the list is traversed).

@@

\begin{wrapfigure}{r}{.25\textwidth}
\scalebox{0.5}{
\begin{tabular}{c}
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(50,8) %\psframe(0,-5)(40,8)
  \putnode{t0}{origin}{5}{0}{\var{\Lanv{\pa}{}}} \putnode{t1}{t0}{9}{0}{\pscirclebox{\mbox{\ \ \ \
  }}} \hspace{5mm} \putnode{t2}{t1}{12}{0}{\pscirclebox{\mbox{\  \ \ \
  }}}
  \psset{arrows=->} \ncline{t0}{t1} \ncline{t1}{t2} \putnode{l0}{t1}{5}{2}{\clazy}
  \putnode{tD1}{t2}{12}{0}{\pscirclebox[doubleline=true]{\mbox{\       \       \       \
  }}} 
  \psset{arrows=->} \ncline{t2}{tD1} \putnode{l1}{t2}{5}{2}{\bcar}
  \nccurve[angleA=45,
  angleB=135,                                                 ncurv=4,
  nodesep=-1]{tD1}{tD1} \putnode{lD1}{tD1}{0}{10}{\acdr}
\end{pspicture} 
\\
(a)
\\
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(50,8) %\psframe(0,-5)(40,8)
  \putnode{t0}{origin}{5}{0}{\var{\Lanv{\pa}{}}} \putnode{t1}{t0}{9}{0}{\pscirclebox{\mbox{\ \ \ \
  }}} 
  \hspace{5mm} 
  \putnode{t2}{t1}{12}{0}{\pscirclebox{\mbox{\  \ \ \  }}}
  \psset{arrows=->} \ncline{t0}{t1} \ncline{t1}{t2} 
\end{pspicture}
\\
(b)
\\
\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
\begin{pspicture}(0,-5)(50,8) %\psframe(0,-5)(40,8)
  \putnode{t0}{origin}{5}{0}{\var{\Lanv{\pa}{}}} \putnode{t1}{t0}{9}{0}{\pscirclebox{\mbox{\ \ \ \
  }}} \hspace{5mm} \psset{arrows=->} \ncline{t0}{t1}
\end{pspicture}
\\ 
(c)
\end{tabular}}
 \caption{(a) grammar  rules for \var{\Lanv{\pa}{}} converted  into an
  automaton and  its DFAs after simplification.}\label{fig:main1}
\end{wrapfigure}

If the expression at $\pi_{12}$ in the main program in Figure~\ref{fig:main-pgm1} was 
$\CAR~\pc$, then the liveness of $\pc$ would be $(\clazy\sigma_{all}, \acar\sigma_{all})$.
